\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Anton}
\familyname{Tursenev}
\address{}{Moscow, Russia}
\mobile{+7 925 195 44 90}
\email{anton@rikishi.info}
\homepage{https://rikishi.info}
\extrainfo{Software should be beautiful. Both inside and outside.}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% \setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{10pt}
\renewcommand{\arraystretch}{1.5}

\begin{document}
\maketitle
\section{Best skills and what I want to do}
  \cvline
    {Skills}{
      Building customised websites to the highest specifications.
      Working under pressure and to tight deadlines.
      Coming up with solutions to seemingly intractable problems.
      Making recommendations on the use of new and emerging technologies.
      The ability to work on your own with minimum supervision.}
  \cvline
    {What I want to do}{
      Developing useful and interesting projects.
      Working closely with other developers and professionals.
      Improving the skills of the JavaScript.
      Motivating the team to self-development, inspire and organize.}

\section{Technical Skills}

\begin{tabular}{ l||m{4cm}|m{4cm}|m{4cm}|  }
  & Less than 2 years & From 2 to 5 years & More than 5 years \\
  \hline\hline
  Languages & Go & Node.js & JavaScript, HTML, CSS, PHP \\
  \hline
  Frameworks & Electron, React Native, Vue, Laravel & React, Redux/Flux & jQuery \\
  \hline
  Techniques & & & TDD, DDD, Scrum, Kanban \\
  \hline
  DBMS & & PostgreSQL, MySQL & \\
  \hline
  VCS & & Git, SVN & \\
  \hline
\end{tabular}

\section{Additional Skills}
  \cvline
    {English}{IELTS score 6}

\section{Education}
  \subsection{University}
  \cventry
    {Sep 2002 - Jun 2007}
    {Master of Computer Applications (M.C.A.), Computer science}
    {\newline Vyatka State University, Kirov, Russia}
    {}{}
    {Studied Computer Science with some focus Artificial Intelligence.}

\newpage

\section{Experience}
\cventry
  {Jul 2018 - Present}
  {Frontend developer}
  {Prosto.Insure LLC, Moscow, Russia}
  {\newline{}\url{https://prosto.insure}}{}
  {Development of interfaces for online comparison and purchase of insurance services.}
\cventry
  {Mar 2018 - Present}
  {Web developer}
  {Fonseka Innovations Pty. Ltd., Brisbane, Australia}
  {\newline{}\url{https://fonsekainnovations.com}}{}
  {Design, develop, test and deploy web and mobile applications.}
\cventry
  {Dec 2016 - Dec 2017}
  {Frontend developer}
  {Mail.Ru LLC, Moscow, Russia}
  {\newline{}\url{https://mail.ru}}{}
  {Development the user interface of the web version of the calendar.}
\cventry
  {Jan 2013 - Dec 2016}
  {Team leader of the group for development of interfaces for postal services}
  {Yandex LLC, Moscow, Russia}
  {\newline{}\url{https://yandex.com}}{}
  {Development the user interface of the web version of the e-mail and other related projects.
  Organization of development in the team.\newline{}
  Training of new developers.}
\cventry
  {Apr 2006 - Dec 2012}
  {Web developer}
  {Lightsoft Research LLC, Moscow, Russia}
  {\newline{}\url{http://lightsoft.com}}{}
  {Development of server and client side projects for tourism.\newline{}
  Organization of development in the team.\newline{}
  Training of new developers.}

\section{Projects}
  \subsection{Commercial Projects}
  \cvline
    {Mail}
    {\url{https://mail.yandex.com}\newline{}
    \textbf{Web client for e-mail.}\newline{}
    Participation in the development the user interface of the web version of the e-mail.\newline{}
    Organization of development in the team.\newline{}
    Refactoring and optimization.\newline{}
    Training of new developers.}
  \cvline
    {Connect}
    {\url{https://connect.yandex.com}\newline{}
    \textbf{Set of services for teamwork: e-mail, messenger, calendar, etc.}\newline{}
    Participation in the development the user interface of the web version of the messenger
    \url{https://yamb.yandex.com}.\newline{}
    Organization of development in the team.\newline{}
    Refactoring and optimization.}
  \cvline
    {Calendar}
    {\url{https://calendar.mail.ru}\newline{}
    \textbf{Web client for calendar.}\newline{}
    Participation in the development the user interface of the web version of the calendar.\newline{}
    Refactoring and optimization.}
  \cvline
    {TopHotels}
    {\url{https://tophotels.org}\newline{}
    \textbf{Information rating of hotels.}\newline{}
    Participation in the development of the server and client side of the project.\newline{}
    Organization of development in the team.}
  \cvline
    {TurPoisk}
    {\url{http://turpoisk.ru}\newline{}
    \textbf{System of search and booking of tours.}\newline{}
    Participation in the development of the server and client side of the project.}
  \cvline
    {TourIndex}
    {\url{https://tourindex.ru}\newline{}
    \textbf{Search system for tours for travel agencies and tourists.}\newline{}
    Participation in the development of the server and client side of the project.}
  \cvline
    {AgClaims}
    {\url{https://play.google.com/store/apps/details?id=com.agclaims}\newline{}
    \textbf{AgClaims inspection app is a dedicated crop assessing app for agricultural insurance claims.}\newline{}
    Development of new functionality. Fix bugs, troubleshoot and resolve problems.}
  \subsection{OpenSource Projects}
  \cvline
    {XBubbles}
    {\url{https://katochimoto.github.io/x-bubbles/}\newline{}
    \textbf{Creating a set of editable elements.}\newline{}
    The launch of the project.}
  \cvline
    {CKEditor for Yandex.Mail}
    {\url{https://yandex-ui.github.io/ckeditor/}\newline{}
    \textbf{The editor for editing e-mails.}\newline{}
    Adaptation and revision of the editor for editing e-mails.\newline{}
    My contribution:\newline{}
    \url{https://github.com/yandex-ui?q=ckeditor}
    }
  \cvline
    {Xblocks}
    {\url{https://katochimoto.github.io/xblocks/}\newline{}
    \textbf{HTML custom elements on the basis React and X-Tag.}\newline{}
    The launch of the project.}

\section{Public Activity}
  \subsection{On the Internet}
    \cvline{Site}{\url{https://rikishi.info}}
    \cvline{GitHub}{\url{https://github.com/Katochimoto}}
    \cvline{LinkedIn}{\url{https://linkedin.com/in/rikishi}}

\end{document}
