\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Anton}
\familyname{Tursenev}
\address{}{Thailand, Chon Buri}
\mobile{TH +66 62 770 2074}
\email{anton@rikishi.info}
\homepage{rikishi.info}
% \extrainfo{Software should be beautiful. Both inside and outside.}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% \setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{10pt}
\renewcommand{\arraystretch}{1.5}

\begin{document}
\maketitle
\section{Best skills and what I want to do}
  \cvline
    {Skills}{
      Building customised websites to the highest specifications.
      Working under pressure and to tight deadlines.
      Coming up with solutions to seemingly intractable problems.
      Making recommendations on the use of new and emerging technologies.
      The ability to work on your own with minimum supervision.}
  \cvline
    {What I want to do}{
      Developing useful and interesting projects.
      Working closely with other developers and professionals.
      Improving the skills of the JavaScript.
      Motivating the team to self-development, inspire and organize.}

\section{Technical Skills}

\begin{tabular}{ l||m{4cm}|m{4cm}|m{4cm}|  }
  & Less than 2 years & From 2 to 5 years & More than 5 years \\
  \hline\hline
  Languages & Go, TypeScript & Node.js, PHP & JavaScript, HTML, CSS \\
  \hline
  Frameworks & Electron, React Native, Laravel, Meteor & Redux/Flux, Vue.js, WatermelonDB, RxJS & React \\
  \hline
  Techniques & & & TDD, DDD, Scrum, Kanban \\
  \hline
  DBMS & & PostgreSQL, MySQL, MongoDB & \\
  \hline
\end{tabular}

\section{Additional Skills}
  \cvline
    {English}{IELTS score 6}

\section{Education}
  \subsection{University}
  \cventry
    {Sep 2002 - Jun 2007}
    {Master of Computer Applications (M.C.A.), Computer science}
    {\newline Vyatka State University, Kirov, Russia}
    {}{}
    {Studied Computer Science with some focus Artificial Intelligence.}

\newpage

\section{Experience}
\cventry
  {Sep 2018 - Present}
  {Frontend developer}
  {WIZATA S.A., Luxembourg}
  {\newline{}\url{https://www.wizata.com}}{}
  {Development of the user interface of Wizata Platform, a platform for digital transformation of the manufacturing process.\newline{}
  Technologies: React, WatermelonDB, Vue.js, RxJS.}
\cventry
  {Aug 2019 - Aug 2021}
  {Frontend developer}
  {Amilabs Company Limited, Bangkok, Thailand}
  {\newline{}\url{https://amilabs.pro}}{}
  {Development of the user interface of Everex Cash digital wallet (everex.cash) and Ethereum tokens explorer (ethplorer.io).\newline{}
  Technologies: React, Meteor, MongoDB.}
\cventry
  {Mar 2018 - Aug 2018}
  {Web developer}
  {Fonseka Innovations Pty. Ltd., Brisbane, Australia}
  {\newline{}\url{https://fonsekainnovations.com}}{}
  {Development the dedicated crop assessing application AgClaims for agricultural insurance claims.\newline{}
  Took part in application development for the purchase of insurance programs.\newline{}
  Technologies: React, React Native, Realm, Vue.js, Vuex.}
\cventry
  {Dec 2016 - Dec 2017}
  {Frontend developer}
  {Mail.Ru LLC, Moscow, Russia}
  {\newline{}\url{https://mail.ru}}{}
  {Development the user interface of the web version of the Calendar.\newline{}
  Participated in the development of services for business.\newline{}
  Development the library of UI components. Client optimization.\newline{}
  Technologies: React, Vanilla JS, homemade MVC framework, Karma, Electron, etc.}
\cventry
  {Jan 2013 - Dec 2016}
  {Frontend developer, Team leader of the group for development of interfaces for postal services}
  {Yandex LLC, Moscow, Russia}
  {\newline{}\url{https://yandex.com}}{}
  {Development the user interface of the web version of the Mail (mail.yandex.com).\newline{}
  Development of new services for teamwork (connect.yandex.com).\newline{}
  Optimization for old browsers. Client optimization. Writing tests.\newline{}
  Training of new developers. Organization of development in the team.\newline{}
  Technologies: Node.js, React, Redux, Immutable.js, Noscript (homemade MVC framework), Karma, Ckeditor, Custom Elements, Vanilla JS, WebSocket, WebRTC, etc.}
\cventry
  {Apr 2006 - Dec 2012}
  {Web developer}
  {Lightsoft Research LLC, Moscow, Russia}
  {\newline{}\url{http://lightsoft.com}}{}
  {Development of server and client side projects for tourism.\newline{}
  Development of the project information database of hotels (TopHotels).\newline{}
  Participated in the development of search system for tours for travel agencies and tourists (TourIndex, TurPoisk).\newline{}
  Project development for cross-authorization between company projects (AgentPassport).\newline{}
  Database design and optimization, migration from Oracle/MySQL to PostgreSQL. Configuring servers, load balancing, SEO/client optimization.\newline{}
  Organization of development in the team. Training of new developers.\newline{}
  Technologies: PHP, PostgreSQL, MySQL, RabbitMQ, Nginx, Vanilla JS}

\newpage

\section{Projects}
  \subsection{Commercial Projects}
  \cvline
    {Wizata Platform}
    {\url{https://www.wizata.com/platform}\newline{}
    \textbf{Digital Twin of manufacturing process.}\newline{}
    Development of the user interface of the platform. Performance optimization. Increase application availability.\newline{}
    Improving skills of creation PWA and offline first applications, working with offline database WatermelonDB, and improving skills of Vue.js and React.}
  \cvline
    {Ethplorer}
    {\url{https://ethplorer.io}\newline{}
    \textbf{Ethereum tokens explorer.}\newline{}
    Development of the user interface of the tokens explorer. Performance optimization. Implemented UI for tokens watching service, labels, charts and profile.\newline{}
    Improving skills of React, Meteor and MongoDB.}
  \cvline
    {Everex Cash}
    {\url{https://everex.cash}\newline{}
    \textbf{Digital wallet.}\newline{}
    Development of the user interface of the digital wallet. Performance optimization, bug fixes, stability improvement.\newline{}
    Improving skills of React, Meteor and MongoDB.}
  \cvline
    {Mail}
    {\url{https://mail.yandex.com}\newline{}
    \textbf{Web client for e-mail.}\newline{}
    Development of a highly loaded project. Refactoring and optimization.\newline{}
    Organization of development in the team. Hiring and training of new developers.}
  \cvline
    {Connect}
    {\url{https://connect.yandex.com}\newline{}
    \textbf{Set of services for teamwork: e-mail, messenger, calendar, etc.}\newline{}
    Development of the project from scratch using modern technologies:
    React/Redux, WebSockets, Immutable data, etc.
    Organization of development in a team of 4 people.}
  \cvline
    {AgClaims}
    {\url{https://play.google.com/store/apps/details?id=com.agclaims}\newline{}
    \textbf{AgClaims inspection app is a dedicated crop assessing app for agricultural insurance claims.}\newline{}
    Getting experience of development on React Native.}
  \cvline
    {Calendar}
    {\url{https://calendar.mail.ru}\newline{}
    \textbf{Web client for calendar.}\newline{}
    Participation in the development the user interface of the web version of the calendar.\newline{}
    Refactoring and optimization. Improving the skills of native JS.}
  \cvline
    {TopHotels}
    {\url{https://tophotels.org}\newline{}
    \textbf{Information rating of hotels.}\newline{}
    Development of a highly loaded project.
    Getting skills to work with PHP and PostgreSQL: optimization, database design.
    Configuring servers, load balancing, SEO optimization.}

\newpage

  \subsection{Personal Projects}
  \cvline
    {MonadA Pool}
    {\url{https://monada.digital}\newline{}
    \textbf{Staking Pool for Cardano blockchain.}\newline{}
    Getting skills working with Ansible, Cardano blockchain. Set up, monitor, maintain and support staking pool.}
  \cvline
    {MonadA Gallery}
    {\url{https://monada.gallery}\newline{}
    \textbf{NFT Marketplace for Cardano blockchain.}\newline{}
    Build NFT marketplace from scratch. Create frontend, backend, UX/UI, design. Getting skills working with Ansible, Nodejs, Cardano blockchain.}

\section{Public Activity}
  \subsection{On the Internet}
    \cvline{Site}{\url{https://rikishi.info}}
    \cvline{GitHub}{\url{https://github.com/Katochimoto}}
    \cvline{LinkedIn}{\url{https://linkedin.com/in/rikishi}}

\end{document}
