\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Anton}
\familyname{Tursenev}
\address{}{Moscow, Russian Federation}
\mobile{+7 925 1954490}
\email{rikishi@protonmail.ch}
\homepage{https://rikishi.info}
\extrainfo{Software should be beautiful. Both inside and outside.}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle
\section{Projects}
  \subsection{Commercial Projects}
  \cvline
    {Mail}
    {\url{https://mail.yandex.ru}\newline{}
    \textbf{Web client for email.}\newline{}
    Develop user interface of web version of the email.\newline{}
    Organization of development in the team.}
  \cvline
    {Connect}
    {\url{https://connect.yandex.ru}\newline{}
    \textbf{A set of services for teamwork: email, wiki, calendar, etc.}\newline{}
    ...}
  \cvline
    {Calendar}
    {\url{https://calendar.mail.ru}\newline{}
    \textbf{Web client for calendar.}\newline{}
    Develop user interface of web version of the calendar.}
  \cvline
    {TopHotels}
    {\url{https://tophotels.ru}\newline{}
    \textbf{Information rating of hotels.}\newline{}
    Database migration from Oracle to Mysql and later on Postgresql.}
  \cvline
    {TurPoisk}
    {\url{http://turpoisk.ru}\newline{}
    \textbf{System of search and booking of tours.}\newline{}
    ...}
  \cvline
    {TourIndex}
    {\url{https://tourindex.ru}\newline{}
    \textbf{Search system for tours for travel agencies and tourists.}\newline{}
    ...}
  \cvline
    {TravelInform}
    {\url{http://travelinform.ru}\newline{}
    \textbf{Constantly updated relevant and important information of the tourist market from around the world.}\newline{}
    ...}
  \cvline
    {TravelPassport}
    {\url{https://travelpassport.ru}\newline{}
    \textbf{A unified system of authorization on tourist sites.}\newline{}
    The launch of the project.}
  \cvline
    {AgentPassport}
    {\url{http://agentpassport.ru}\newline{}
    \textbf{A unified system of authorization on tourist sites for travel agencies.}\newline{}
    The launch of the project.}
  \cvline
    {HotelsPassport}
    {\url{http://hotelspassport.com}\newline{}
    \textbf{Service management system for hoteliers.}\newline{}
    The launch of the project.\newline{}
    Multilingual content editing. Connecting external translators.}
  \subsection{OpenSource Projects}
  \cvline
    {XBubbles}
    {\url{https://katochimoto.github.io/x-bubbles/}\newline{}
    \textbf{...}\newline{}
    ...}
  \cvline
    {CKEditor for Yandex.Mail}
    {\url{https://yandex-ui.github.io/ckeditor/}\newline{}
    \textbf{...}\newline{}
    ...\newline{}
    My contribution:\newline{}
    \url{https://github.com/yandex-ui?q=ckeditor}
    }
  \cvline
    {Xblocks}
    {\url{http://xblocks.info}\newline{}
    \textbf{HTML custom elements on the basis React and X-Tag.}\newline{}
    ...}
  \cvline
    {Calendar}
    {\url{https://yandex-ui.github.io/calendar/}\newline{}
    \textbf{...}\newline{}
    ...}
\pagebreak
\section{Experience}
\cventry
  {Jul 2016 - Present}
  {Software developer}
  {Uberchord, Berlin, Germany}
  {\newline{}\url{https://www.uberchord.com}}{}
  {Maintaining existing app: implementing new features, fixing bugs.}
\cventry
  {Sep 2014 - Jun 2016}
  {Software developer}
  {Blacklane, Berlin, Germany}
  {\newline{}\url{https://blacklane.com}}{}
  {Maintaining existing apps: implementing new features, fixing bugs.}
\cventry
  {May 2013 - Aug 2014}
  {Software engineer}
  {Railsware, Kiev, Ukraine}
  {\newline{}\url{http://railsware.com}}{}
  {Assessment of requirements for software development and time estimation.\newline{}
  Taught backend developers how to write iOS apps and learned from backend developers how to write backends.}
\cventry
  {Oct 2012 - Mar 2013}
  {iOS developer}
  {Stanfy LLC. Kiev, Ukraine}
  {\newline{}\url{http://stanfy.com}}{}
  {Assessment of requirements for software development and time estimation.
  \newline{}Software development.}
\cventry
  {Feb 2011 - Oct 2012}
  {iOS/RubyOnRails developer}
  {MLSDev LLC. Donetsk, Ukraine}
  {\newline{}\url{http://mlsdev.com}}{}
  {Assessment of requirements for software development and time estimation.\newline{}
  Software development. Web-services deployment and support.}
\cventry
  {Aug 2010 - Feb 2011}
  {C++/Qt developer}
  {WiseTroll (Sole Proprietorship). Donetsk, Ukraine}
  {}{}
  {Assessment of requirements for software development and time estimation.
  \newline{}Software development.}

\section{Technical Skills}
\cvline
  {Languages}{JS, HTML, CSS, PHP}
\cvline
  {Languages}{PostgreSQL}
\cvline
  {VCS}{Git, SVN}
\cvline
  {OS}{OS X, Linux (Ubuntu)}
\cvline
  {Techniques}{TDD, DDD, Scrum, Kanban}
\cvline
  {Frameworks}{React, Redux, Flux, Electron}

\section{Education}
  \subsection{University}
  \cventry
    {Oct 2006 - Dec 2011}
    {Software Development}
    {Computer Academy "Step", Donetsk, Ukraine}
    {}{}
    {Team member, represented Ukraine at the final of ImagineCup'10 at Poland.}
  \cventry
    {Sep 2006 - Jul 2010}
    {Management of Organizations, Bachelor}
    {Open International University of Human Development "Ukraine"}
    {}{}{}
  \subsection{MOOCs (Coursera)}
  \cventry
    {Sep 2015 - Nov 2015}
    {Automata}
    {\newline Learned a lot about automata, regular languages, grammars \&c.}
    {}{\newline\url{https://www.coursera.org/course/automata}}{}
  \cventry
    {Apr 2015 - Jun 2015}
    {From Nand to Tetris / Part I}
    {\newline Learned basics of logic circuits. Implemented Assembler for a 'toy' machine}
    {}{\newline\url{https://www.coursera.org/course/nand2tetris1}}{}
  \cventry
    {Sep 2014 - Nov 2014}
    {Functional Programming Principles in Scala}
    {\newline Learned basics of functional programming}
    {}{\newline\url{https://www.coursera.org/course/progfun}}{}

\section{Public Activity}
  \subsection{Speaking}
  \cventry
    {FOSDEM 2017}
    {Mutation Testing: Leaving the stone age}
    {}
    {}{}
    {Link: \url{https://fosdem.org/2017/schedule/event/mutation_testing/}}
  \cventry
    {RIT++ 2016}
    {Getting started with LLVM using Swift}
    {}
    {}{}
    {Link: \url{http://appsconf.ru/2016/abstracts/2165}}
  \cventry
    {FOSDEM 2016}
    {How to use LLVM C API with Swift}
    {}
    {}{}
    {Link: \url{https://fosdem.org/2016/schedule/event/llvm_c_swift/}}
  \cventry
    {Mobile Warsaw}
    {Magic Behind Xcode}
    {Compilation}
    {}{}
    {Slides: \url{https://speakerdeck.com/alexdenisov/magic-behind-xcode}}
  \cventry
    {CocoaHeads Berlin}
    {Compilation Process}
    {How a program is born}
    {}{}
    {Slides: \url{https://speakerdeck.com/alexdenisov/compilation-process}}
  \cventry
    {CocoaHeads Berlin}
    {BloodMagic}
    {Custom property attributes for Objective-C}
    {}{}
    {Slides: \url{https://speakerdeck.com/alexdenisov/bloodmagic}}
  \subsection{On the Internet}
    \cvline{Blog}{\url{https://rikishi.info}}
    \cvline{GitHub}{\url{https://github.com/Katochimoto}}
    \cvline{npmjs}{\url{https://npmjs.com/~rikishi}}
    \cvline{LinkedIn}{\url{https://linkedin.com/in/rikishi}}

\end{document}
